Arjun Shanmugam's Senior Thesis

### 2023-01-10 writing/paper/main.tex

\usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,multicol, multirow,natbib,pdflscape,subfigure,array,hyperref, pdflscape}

@@

\onehalfspacing
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}{Proposition}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newtheorem{hyp}{Hypothesis}
\newtheorem{subhyp}{Hypothesis}[hyp]
\renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}

\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}m{#1}}

@@

\section{Introduction} \label{sec:introduction}
\subsection{Literature Review}

\section{Institutional Context}
    \subsection{Eviction in Massachusetts}
        \subsubsection{The Massachusetts Housing Court}
        \subsubsection{The Eviction Process}
    \subsubsection{Property Tax Assessment}
        \subsubsection{The Property Value Assessment Process}
    \subsection{Zestimates}
        \subsubsection{How Are Zestimates Produced?}
        \subsubsection{Reliability}
\section{Data} \label{sec:data}
    \begin{landscape}
    \subsection{Evictions Data}
        \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/evictions_map.png}
            \caption{Spatial Incidence of Eviction}
            \label{fig:my_label}
        \end{figure}
    \end{landscape}
    \subsection{Tax Assessment Records}
    \subsection{Zestimates}
        \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/trends_in_zestimates.png}
            \caption{Trends in Zestimates}
            \label{fig:my_label}
        \end{figure}
    \begin{landscape}
    \subsection{Summary Statistics}
         \begin{table}[H]
            \centering
            \tiny
            \input{output/summary_statistics/tables/summary_statistics.tex}
            \caption{Summary Statistics}
            \label{tab:table_1}
        \end{table}
        \newpage
        \begin{table}[H]
            \centering
            \tiny
            \input{output/summary_statistics/tables/balance_table.tex}
            \caption{Balance Table}
            \label{tab:my_label}
        \end{table}
    \end{landscape}

\section{Empirical Strategy: Difference-in-Difference}
    \subsection{Estimating the ATT in the Staggered Treatment Case}
    I will use Callaway and Sant'Anna' (2021)'s multiperiod, staggered treatment difference-in-difference estimators. The following bullets summarize the empirical strategy informally; this information will eventually be placed appropriately into the subsection headers below this brief summary.
    \begin{enumerate}
        \item Reject conventional TWFE-DiD estimator. This estimator essentially estimates the ATT by performing a bunch of 2 unit, 2 period DiDs, then averages the calculated treatment effects. Goodman-Bacon (2021) shows that this estimator is composed in part of DiD estimates involving \emph{two units which are both treated during both periods}. This is in violation of the spirit of DiD. These incorrect DiD estimates are known as ``forbidden comparisons.''
        \item The way to properly recover the ATT is to basically perform all of the ``non-forbidden'' comparisons possible in our panel dataset. More formally:
        \begin{enumerate}
            \item We begin with a panel dataset of properties whose Zestimates are observed monthly. At each property $i$, an eviction case concludes during month $G_i=g$, resulting in a plaintiff victory or a defendant victory. These properties are collectively known as ``cohort $g$.'' If the eviction case at property $i$ resulted in a defendant victory, let $C_i=1$
            \item Break the units into ``cohorts'' according to the month in which their cases conclude. 
            \item We estimate $ATT(g, t)$, which is the average treatment effect on the treated for cohort $g$ at time $t$, by calculating the sample analog of:

@@

            \end{enumerate}
        \item Now, we have a bunch of $ATT(g, t)$s. How do we aggregate them?
            \begin{enumerate}
                \item Take frequency-weighted averages across $t$ to get $ATT(g)$s, or ATTs for each cohort.
                \item Take frequency-weighted averages across $g$ to get $ATT(t)$s, or ATTs for each time period.
                \item Most convincing: calculate event time $e = t - g$. Now, $ATT(g, e_i)$ expresses the ATT on cohort $g$ at time relative to the end of the eviction case involving property $i$. Take frequency weighted averages across $g$ to get $ATT(e)s$, or ATTs for each period relative to the treatment period.
            \end{enumerate}
    \end{enumerate}
    \subsection{Parallel Trends Assumptions in the Staggered Treatment Case}

>>>>

\usepackage{amssymb,amsmath,amsfonts,booktabs,eurosym,float,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,multicol, multirow,natbib,pdflscape,subfigure,array,hyperref, pdflscape}
\bibliographystyle{unsrtnat}

@@

@@

\section{Introduction} \label{sec:introduction}
\bibliography{writing/paper/citations}
\subsection{Literature Review}

\section{Institutional Context}
    \subsection{Eviction in Massachusetts}
        \subsubsection{The Massachusetts Housing Court}
        \subsubsection{The Eviction Process}
    \subsection{Property Tax Assessment}
        \subsubsection{The Property Value Assessment Process}
    \subsection{Zestimates}
        \subsubsection{How Are Zestimates Produced?}
        \subsubsection{Reliability}
\section{Data} \label{sec:data}
    \begin{landscape}
    \subsection{Evictions Data}
        \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/evictions_map.png}
            \caption{Spatial Incidence of Eviction}
            \label{fig:my_label}
        \end{figure}

        \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/filings_over_time.png}
            \caption{Eviction Filings Over Time}
            \label{fig:my_label}
        \end{figure}
    \end{landscape}
        \begin{table}[H]
            \centering
            \input{output/summary_statistics/tables/treatment_timings.tex}
            \caption{Distribution of Eviction Filings and Outcomes}
            \label{tab:my_label}
        \end{table}

    \subsection{Tax Assessment Records}
    \subsection{Zestimates}
        \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/trends_in_zestimates.png}
            \caption{Trends in Zestimates}
            \label{fig:my_label}
        \end{figure}
    \begin{landscape}
    \subsection{Summary Statistics}
         \begin{table}[H]
            \centering
            \small
            \input{output/summary_statistics/tables/summary_statistics.tex}
            \caption{Summary Statistics}
            \label{tab:table_1}
        \end{table}
        \newpage
        \begin{table}[H]
            \centering
            \small
            \input{output/summary_statistics/tables/balance_table.tex}
            \caption{Balance Table}
            \label{tab:my_label}
        \end{table}
    \end{landscape}

\section{Empirical Strategy: Difference-in-Difference}
    I seek to estimate average treatment effects of plaintiff victory on treated properties. Let $G_i$ be the treatment cohort for eviction case $i$; $G_i = g \in \{\text{May}\:2019, \text{June}\:2019, ..., \text{May}\:2021\}$ if eviction case $i$ resulted in a victory for the plaintiff. Let $C_i = 1$ if eviction case $i$ resulted in a victory for the defendant and $0$ otherwise. I use  the staggered difference-in-difference estimator proposed in \cite{callaway_sant'anna_2021}, which estimates time- and cohort-specific average treatment effects on the treated using canonical difference-in-difference estimators and then aggregates them, weighting by cohort size, to produce summaries of the average treatment effect on the treated.

    \subsection{Estimating the ATT in the Staggered Treatment Case}
    I will use Callaway and Sant'Anna' (2021)'s multiperiod, staggered treatment difference-in-difference estimators. The following bullets summarize the empirical strategy informally; this information will eventually be placed appropriately into the subsection headers below this brief summary.
    \begin{enumerate}
        \item Reject conventional TWFE-DiD estimator. This estimator essentially estimates the ATT by performing a bunch of 2 unit, 2 period DiDs, then averages the calculated treatment effects. Goodman-Bacon (2021) shows that this estimator is composed in part of DiD estimates involving \emph{two units which are both treated during both periods}. This is in violation of the spirit of DiD. These incorrect DiD estimates are known as ``forbidden comparisons.''
        \item The way to properly recover the ATT is to basically perform all of the ``non-forbidden'' comparisons possible in our panel dataset. More formally:
        \begin{enumerate}
            \item We begin with a panel dataset of properties whose Zestimates are observed monthly. At each property $i$, an eviction case concludes during month $G_i=g$, resulting in a plaintiff victory or a defendant victory. These properties are collectively known as ``cohort $g$.'' If the eviction case at property $i$ resulted in a defendant victory, let $C_i=1$
            \item Break the units into ``cohorts'' according to the month in which their cases conclude. 
            \item We estimate $ATT(g, t)$, which is the average treatment effect on the treated for cohort $g$ at time $t$, by calculating the sample analog of:

@@

            \end{enumerate}
        \item Now, we have a bunch of $ATT(g, t)$s. How do we aggregate them?
            \begin{enumerate}
                \item Take frequency-weighted averages across $t$ to get $ATT(g)$s, or ATTs for each cohort.
                \item Take frequency-weighted averages across $g$ to get $ATT(t)$s, or ATTs for each time period.
                \item Most convincing: calculate event time $e = t - g$. Now, $ATT(g, e_i)$ expresses the ATT on cohort $g$ at time relative to the end of the eviction case involving property $i$. Take frequency weighted averages across $g$ to get $ATT(e)s$, or ATTs for each period relative to the treatment period.
            \end{enumerate}
    \end{enumerate}

    \newpage
    \begin{landscape}
       \begin{table}[H]
        \centering
        \input{output/DiD/tables/balance_table.tex}
        \caption{Caption}
        \label{tab:my_label}
    \end{table} 
    \end{landscape}

    \subsection{Parallel Trends Assumptions in the Staggered Treatment Case}
